Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
Ana

In their work, the main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking at what clones we \textbf{should} refactor. We propose definitions for refactorable clones together with thresholds to be able to limit their impact negative on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

@@

\section{Discussion}
In this section, we discuss the results of our experiments.

@@

We defined two aspects as part of the context of a clone: relation and location. Regarding relations, we found that most clones are found in the same class, over 37\%. About 24\% of clones are in the same inheritance hierarchy. Another 24\% of clones are unrelated. The final 7\% of clones have the same interface. Regarding location, over 74\% of clones span part of a method. About 8\% span several methods. Only 4\% of clones span a declaration (method, class, etc.) fully.

We built a tool that can automatically apply refactorings to 28\% of clones in our corpus using the ``Extract Method'' refactoring technique. The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside a method is part of a clone.

>>>>

In their work, the main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

@@

\section{Discussion}
%In this section, we discuss the results of our experiments.

@@

We defined two aspects as part of the context of a clone: relation and location. Regarding relations, over 37\% of clones are found in the same class. About 24\% of clones are in the same inheritance hierarchy. Another 24\% of clones are unrelated. The final 15\% of clones have the same interface. Regarding location, over 74\% of clones span part of a method. About 8\% span several methods. Only 4\% of clones span a declaration (method, class, etc.) fully.

We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique. The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
